Develop atlantisom wrappers

### 2020-01-13 WrapperDevelopment.Rmd
add details

1. initialize: locate model output (function to make a config file?), read in basic run parameters and species names, run_truth for all once and save output (optionally, run_truth for only one species?)

@@

@@

>>>>

1. initialize: locate model output (function to make a config file?), read in basic run parameters and species names, run_truth for all once and save output

  + User to make up front decision--want all species or just a subset?
  + May want multiple species that need to be split in a later step for models

@@

  + Based on decision above, save interim steps for use later
  + Need a switch for single vs multispecies estimation models?

@@

## Cumbersome giant files eat all the memory!

Implement Christine's memory saving things from the NEMOW demo
